Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-22 paper/ijcai/paper.tex
up to 5.2 (excluding)

  \begin{subfigure}{0.5\textwidth}
    \centering
    \begin{tabular}{cccccc}
      1 & $c_4$ (0.59) & & 1 & $c_2$ (0.35) \\
      2 & $c_3$ (0.55) & & 2.5 & $c_1$ (0.32)\\
      3 & $c_2$ (0.35) & \hspace{1ex}$\Rightarrow$\hspace{1ex} & 2.5 & $c_5$ (0.32)\\
      4.5 & $c_1$ (0.32) & & 4 & $c_3$ (0.29)\\
      4.5 & $c_5$ (0.32) & & 5 & $c_4$ (0.00)\\
    \end{tabular}
    \caption{Ranking update.}
  \end{subfigure}

@@

The first question evaluates the ability of dynamic slicing reducing
application code. Improvements on fault localization depends on that
ability. The second question addresses the problem that affects all
dynamic slicing techniques~\cite{Lin:2018:BDE:3238147.3238163}---that
of missing faulty statements (see
Section~\ref{sec:slicing}). Developers would not be able to
successfully debug code if that issue is manifested. The third
research question evaluates the impact of the combination as
substantiated by \comb.

@@

%
To evaluate our approach, we compare the cost of diagnosing
a collection of faults using \sfl{} versus \comb{}.
%
\subsection{Objects of Analysis}\label{sec:analysis}

We used the \dfj{} benchmark in our experiments~\cite{just-defects4j-issta2014}.
Originally, this benchmark includes six different subjects and 395 faults (Table
\ref{tab:df4j}). \lang{} is a library that provides a set of helper utilities
for the {\small\texttt{java.lang}} API. \cmath{} is a lightweight library of
self-contained mathematics and statistics components. The \closure{} is a
toolset for turning JavaScript files into smaller scripts for faster download
and execution in the browser. \chart{} is a Java library for creating charts.
\jtime{} is a lightweight library that aims to replace the default Java
{\small\texttt{java.util.Date}} classes providing simpler APIs. \mockito{} is a
mocking testing framework.

\newcommand{\cgray}[1]{\cellcolor{gray!25}#1}
\begin{table}[h]

  \centering
  \setlength{\tabcolsep}{4pt}
    \begin{tabular}{lrrr}
      \toprule
     Project            & Size (LOC) & \# Tests & \# Faults \\ %\comments{& Failing Test Cases &}
      \midrule
      \lang{}            & 111,751  & 6,057 & 65       \\   %\commentst{& 124   &  -}\\
      \cmath{}           & 306,276  & 26,797 & 106     \\   %\comments{& 177   &  -}\\
      \closure{}         & 149,521  & 27,930  & 133     \\   %\comments{& 350   &  -}\\
      \chart{}           & 230,159  & 8,458 & 26      \\  %\comments{& 92    &  -}\\
      \jtime{}           & 141,610  & 3,289 & 27       \\   %\comments{& 76    &  -}\\
      \mockito{}         & 22,787  & 8,835 & 38    \\     %\comments{& 118   &  -}\\
      \bottomrule
  \end{tabular}
\caption {Characterization of \dfj{} subjects.}

\label{tab:df4j}
\end{table}
\normalsize

\begin{figure}[h]
  \vspace{-0.5cm}

		\centering
		\includegraphics[width=0.42\textwidth]{figures/defects4j.pdf}
		\vspace{-0.75cm}
		\caption{Faults of omissions' distribution}
		\label{fig:foos}
\end{figure}

Figure~\ref{fig:foos} shows the predominance of Fault Of Omission (FOO) cases in
the dataset, i.e., faults which generally are difficult to locate. $59.7\%$ of
the faults of this dataset are FOOs. \Sof{@todo: Explain better what are FOOs}

@@

@@

\begin{table}[H]
	\centering
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{lcc}
		\toprule
		Project             &  \combpar{5}  & \combpar{10} \\
		\midrule

>>>>

  \begin{subfigure}{0.5\textwidth}
    \centering
    \begin{tabular}{cccccc}
      {\cellcolor{Gray}1} & {\cellcolor{Gray}$c_4$ (0.59)} & & 1 & $c_2$ (0.35) \\
      {\cellcolor{Gray}2} & {\cellcolor{Gray}$c_3$ (0.55)} & & 2.5 & $c_1$ (0.32)\\
      3 & $c_2$ (0.35) & \hspace{1ex}$\Rightarrow$\hspace{1ex} & 2.5 & $c_5$ (0.32)\\
      4.5 & $c_1$ (0.32) & & {\cellcolor{Gray}4} & {\cellcolor{Gray}$c_3$ (0.29)}\\
      4.5 & $c_5$ (0.32) & & {\cellcolor{Gray}5} & {\cellcolor{Gray}$c_4$ (0.00)}\\
    \end{tabular}
    \caption{Ranking update.}
  \end{subfigure}

@@

The first question evaluates the ability of dynamic slicing to reduce
the size of application code. Improvements on fault localization
depend on that ability. The second question addresses the problem that
affects all dynamic slicing
techniques~\cite{Lin:2018:BDE:3238147.3238163}---that of missing
faulty statements (see Theorem~\ref{the:1}). Developers would
not be able to successfully debug code for the cases that issue is
manifested. The third research question evaluates the impact of the
combination, as substantiated by \comb, to fault localization.

@@

%
%
\subsection{Objects of Analysis}\label{sec:analysis}

We used subject programs from the \dfj{}
benchmark~\cite{just-defects4j-issta2014} in our evaluation.
Table~\ref{tab:df4j} shows size, number of tests, and number of
faults, for each considered program.

\begin{table}[h]
  \small  
  \centering
  \setlength{\tabcolsep}{4pt}
  \begin{tabular}{lrrr}
    \toprule
    Project            & Size (LOC) & \# Tests & \# Faults \\ %\comments{& Failing Test Cases &}
    \midrule
    \lang{}            & 111,751  & 6,057 & 65       \\   %\commentst{& 124   &  -}\\
    \cmath{}           & 306,276  & 26,797 & 106     \\   %\comments{& 177   &  -}\\
    %      \closure{}         & 149,521  & 27,930  & 133     \\   %\comments{& 350   &  -}\\
    \chart{}           & 230,159  & 8,458 & 26      \\  %\comments{& 92    &  -}\\
    \jtime{}           & 141,610  & 3,289 & 27       \\   %\comments{& 76    &  -}\\
    \mockito{}         & 22,787  & 8,835 & 38    \\     %\comments{& 118   &  -}\\
    \bottomrule
  \end{tabular}
  \caption {Characterization of \dfj{} subjects.}
  \label{tab:df4j}
\end{table}
\normalsize

\lang{} is a
library that provides a set of helper utilities for the
{\small\texttt{java.lang}} API. \cmath{} is a lightweight library of
self-contained mathematics and statistics components.\comments{ The
  \closure{} is a toolset for turning JavaScript files into smaller
  scripts for faster download and execution in the browser.} \chart{}
is a Java library for creating charts.  \jtime{} is a lightweight
library that aims to replace the default Java
{\small\texttt{java.util.Date}} classes providing simpler
APIs. \mockito{} is a mocking testing framework.

%% Originally, this benchmark includes six different subjects and 395
%% faults (Table \ref{tab:df4j}).

%%%%%%%%%%%%%%%%%%%%% I commented because there are just two cases;
%%%%%%%%%%%%%%%%%%%%% not much information added (that could not be
%%%%%%%%%%%%%%%%%%%%% said in text). -Marcelo
%% \begin{figure}[h]
%%   \vspace{-0.5cm}
%% 		\centering
%% 		\includegraphics[width=0.42\textwidth]{figures/defects4j.pdf}
%% 		\vspace{-0.75cm}
%% 		\caption{Faults of omissions' distribution}
%% 		\label{fig:foos}
%% \end{figure}

As to quantify complexity of fault localization on this dataset, we
additionally counted the number of cases of ``fault of omission'', a
popular metric in fault localization research for that
purpose~\Fix{cite}. A fault of omission occurs when
\Fix{...explain...}. Intuitivelly, the ability of techniques to
produce good diagnosis in those cases reduce as \Fix{...explain...}. A
total of $59.7\%$ of the cases in this dataset manifest fault of
omission, which is a good indication of difficulty.

%in producing
%high-qualitiy diagnosis.

@@

\Fix{
To evaluate our approach, we compare the cost of diagnosing
a collection of faults using \sfl{} versus \comb{}.
}

@@

\begin{table}[H]
  \small
	\centering
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{lcc}
		\toprule
		Project             &  \combpar{5}  & \combpar{10} \\
		\midrule
